---
title: "Social BART descriptives"
output:
  html_document: default
  html_notebook: default
  pdf_document: default
---

## Task
Participants played 6 runs of the BART and S_BART. In Run 1 and 6, participants played Alone BART only. In 2-5 participants played S_BART trials interspersed with Alone BART trials. At the beginning of every run, participants made 3 ratings: 

1. What they think the upper bound of the pop points is, 
2. distributed 50 bets for where they thought the balloon was likely to pop,
3. and distributed 50 bets for where they thought the other participants in that day's session would cash in (only asked in runs 2-5).

Group sizes:

* Competitive: 17
* Non-Competitive: 20

#___________________________________



```{r, include=FALSE}
library(ggplot2)
library(magrittr)
library(lme4)
library(dplyr)

## Gives count, mean, standard deviation, standard error of the mean, and confidence interval (default 95%).
##   data: a data frame.
##   measurevar: the name of a column that contains the variable to be summariezed
##   groupvars: a vector containing names of columns that contain grouping variables
##   na.rm: a boolean that indicates whether to ignore NA's
##   conf.interval: the percent range of the confidence interval (default is 95%)
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
    library(plyr)

    # New version of length which can handle NA's: if na.rm==T, don't count them
    length2 <- function (x, na.rm=FALSE) {
        if (na.rm) sum(!is.na(x))
        else       length(x)
    }

    # This does the summary. For each group's data frame, return a vector with
    # N, mean, and sd
    datac <- ddply(data, groupvars, .drop=.drop,
      .fun = function(xx, col) {
        c(N    = length2(xx[[col]], na.rm=na.rm),
          mean = mean   (xx[[col]], na.rm=na.rm),
          sd   = sd     (xx[[col]], na.rm=na.rm)
        )
      },
      measurevar
    )

    # Rename the "mean" column    
    datac <- rename(datac, c("mean" = measurevar))

    datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean

    # Confidence interval multiplier for standard error
    # Calculate t-statistic for confidence interval: 
    # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
    ciMult <- qt(conf.interval/2 + .5, datac$N-1)
    datac$ci <- datac$se * ciMult

    return(datac)
}

## Norms the data within specified groups in a data frame; it normalizes each
## subject (identified by idvar) so that they have the same mean, within each group
## specified by betweenvars.
##   data: a data frame.
##   idvar: the name of a column that identifies each subject (or matched subjects)
##   measurevar: the name of a column that contains the variable to be summariezed
##   betweenvars: a vector containing names of columns that are between-subjects variables
##   na.rm: a boolean that indicates whether to ignore NA's
normDataWithin <- function(data=NULL, idvar, measurevar, betweenvars=NULL,
                           na.rm=FALSE, .drop=TRUE) {
    library(plyr)

    # Measure var on left, idvar + between vars on right of formula.
    data.subjMean <- ddply(data, c(idvar, betweenvars), .drop=.drop,
     .fun = function(xx, col, na.rm) {
        c(subjMean = mean(xx[,col], na.rm=na.rm))
      },
      measurevar,
      na.rm
    )

    # Put the subject means with original data
    data <- merge(data, data.subjMean)

    # Get the normalized data in a new column
    measureNormedVar <- paste(measurevar, "_norm", sep="")
    data[,measureNormedVar] <- data[,measurevar] - data[,"subjMean"] +
                               mean(data[,measurevar], na.rm=na.rm)

    # Remove this subject mean column
    data$subjMean <- NULL

    return(data)
}


## Summarizes data, handling within-subjects variables by removing inter-subject variability.
## It will still work if there are no within-S variables.
## Gives count, un-normed mean, normed mean (with same between-group mean),
##   standard deviation, standard error of the mean, and confidence interval.
## If there are within-subject variables, calculate adjusted values using method from Morey (2008).
##   data: a data frame.
##   measurevar: the name of a column that contains the variable to be summariezed
##   betweenvars: a vector containing names of columns that are between-subjects variables
##   withinvars: a vector containing names of columns that are within-subjects variables
##   idvar: the name of a column that identifies each subject (or matched subjects)
##   na.rm: a boolean that indicates whether to ignore NA's
##   conf.interval: the percent range of the confidence interval (default is 95%)
summarySEwithin <- function(data=NULL, measurevar, betweenvars=NULL, withinvars=NULL,
                            idvar=NULL, na.rm=FALSE, conf.interval=.95, .drop=TRUE) {

  # Ensure that the betweenvars and withinvars are factors
  factorvars <- vapply(data[, c(betweenvars, withinvars), drop=FALSE],
    FUN=is.factor, FUN.VALUE=logical(1))

  if (!all(factorvars)) {
    nonfactorvars <- names(factorvars)[!factorvars]
    message("Automatically converting the following non-factors to factors: ",
            paste(nonfactorvars, collapse = ", "))
    data[nonfactorvars] <- lapply(data[nonfactorvars], factor)
  }

  # Get the means from the un-normed data
  datac <- summarySE(data, measurevar, groupvars=c(betweenvars, withinvars),
                     na.rm=na.rm, conf.interval=conf.interval, .drop=.drop)

  # Drop all the unused columns (these will be calculated with normed data)
  datac$sd <- NULL
  datac$se <- NULL
  datac$ci <- NULL

  # Norm each subject's data
  ndata <- normDataWithin(data, idvar, measurevar, betweenvars, na.rm, .drop=.drop)

  # This is the name of the new column
  measurevar_n <- paste(measurevar, "_norm", sep="")

  # Collapse the normed data - now we can treat between and within vars the same
  ndatac <- summarySE(ndata, measurevar_n, groupvars=c(betweenvars, withinvars),
                      na.rm=na.rm, conf.interval=conf.interval, .drop=.drop)

  # Apply correction from Morey (2008) to the standard error and confidence interval
  #  Get the product of the number of conditions of within-S variables
  nWithinGroups    <- prod(vapply(ndatac[,withinvars, drop=FALSE], FUN=nlevels,
                           FUN.VALUE=numeric(1)))
  correctionFactor <- sqrt( nWithinGroups / (nWithinGroups-1) )

  # Apply the correction factor
  ndatac$sd <- ndatac$sd * correctionFactor
  ndatac$se <- ndatac$se * correctionFactor
  ndatac$ci <- ndatac$ci * correctionFactor

  # Combine the un-normed means with the normed results
  merge(datac, ndatac)
}

# Multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}


Allsubs.data <- read.csv("~/Documents/S_BART/BART_baseline/Analysis/BART_baseline_analysis/combined_data/Allsubs_BART_Baseline_summarized.csv") %>%
  subset(SubjectID != 96)
Allsubs.dists <- read.csv("~/Documents/S_BART/BART_baseline/Analysis/BART_baseline_analysis/combined_data/Allsubs_BART_Baseline_distributions.csv")
Allsubs.meanSD <- read.csv('~/Documents/S_BART/BART_baseline/Analysis/BART_baseline_analysis/combined_data/Allsubs_BART_Baseline_meanSDdists.csv')

```





### 1. Upper bound of pop points (error bars within-group standard error)
```{r, message=FALSE, warning=FALSE}

noncomp.max.mean <- Allsubs.dists %>%
  subset(Max < 500) %>%
  subset(type == 'pop') %>%
  subset(Competitive == 0) %>%
  summarySEwithin( measurevar="Max", withinvars="run",
                        idvar="SubjID", na.rm=FALSE, conf.interval=.95) %>%
  mutate(Competitive = 'Non-competitive')

Max.mean <- Allsubs.dists %>%
  subset(Max < 500) %>%
  subset(type == 'pop') %>%
  subset(Competitive == 1) %>%
  summarySEwithin( measurevar="Max", withinvars="run",
                        idvar="SubjID", na.rm=FALSE, conf.interval=.95) %>%
  mutate(Competitive = 'Competitive') %>%
  rbind(noncomp.max.mean)

 ggplot(Max.mean, aes(x=factor(run), y=Max, fill=Competitive, group=Competitive)) +
    geom_errorbar(width=.1, aes(ymin=Max-ci, ymax=Max+ci,color=Competitive),alpha = 0.7) +
    geom_point(aes(color = Competitive)) + 
    geom_line(aes(color = Competitive)) +
    ggtitle('Average upper bound estimate distributions (prior to run)') + 
    theme(plot.title = element_text(hjust = 0.5)) + xlab('Run')

```




### 2. Average mean and average SD of subject distributions (error bars within-group standard error)
```{r, message=FALSE, warning=FALSE}

noncomp.pop.mean <- Allsubs.meanSD %>%
  subset(type == 'pop') %>%
  subset(Competitive == 0) %>%
  summarySEwithin( measurevar="mean", withinvars="run",
                        idvar="SubjID", na.rm=FALSE, conf.interval=.95) %>%
  mutate(Competitive = 'Non-competitive')

pop.mean <- Allsubs.meanSD %>%
  subset(type == 'pop') %>%
  subset(Competitive == 1) %>%
  summarySEwithin( measurevar="mean", withinvars="run",
                        idvar="SubjID", na.rm=FALSE, conf.interval=.95) %>%
  mutate(Competitive = 'Competitive') %>%
  rbind(noncomp.pop.mean)

popMean <- ggplot(pop.mean, aes(x=factor(run), y=mean, fill=Competitive, group=Competitive)) +
    geom_errorbar(width=.1, aes(ymin=mean-ci, ymax=mean+ci,color=Competitive),alpha = 0.7) +
    geom_point(aes(color = Competitive)) + 
    geom_line(aes(color = Competitive)) +
    ggtitle('Average Mean of Pop distributions (prior to run)') + 
    theme(plot.title = element_text(hjust = 0.5))


noncomp.pop.SD <- Allsubs.meanSD %>%
  subset(type == 'pop') %>%
  subset(Competitive == 0) %>%
  summarySEwithin( measurevar="SD", withinvars="run",
                        idvar="SubjID", na.rm=FALSE, conf.interval=.95) %>%
  mutate(Competitive = 'Non-Competitive')

pop.SD <- Allsubs.meanSD %>%
  subset(type == 'pop') %>%
  subset(Competitive == 1) %>%
  summarySEwithin( measurevar="SD", withinvars="run",
                        idvar="SubjID", na.rm=FALSE, conf.interval=.95) %>%
  mutate(Competitive = 'Competitive') %>%
  rbind(noncomp.pop.SD)

popSD <- ggplot(pop.SD, aes(x=factor(run), y=SD, fill=Competitive, group=Competitive)) +
    geom_errorbar(width=.1, aes(ymin=SD-ci, ymax=SD+ci,color=Competitive),alpha = 0.7) +
    geom_point(aes(color = Competitive)) + 
    geom_line(aes(color = Competitive)) +
    ggtitle('Average SD of Pop distributions (prior to run)') + 
    theme(plot.title = element_text(hjust = 0.5))

multiplot(popMean,popSD, cols=1)


noncomp.social.mean <- Allsubs.meanSD %>%
  subset(type == 'social') %>%
  subset(Competitive == 0) %>%
  summarySEwithin( measurevar="mean", withinvars="run",
                        idvar="SubjID", na.rm=FALSE, conf.interval=.95) %>%
  mutate(Competitive = 'Non-Competitive')

social.mean <- Allsubs.meanSD %>%
  subset(type == 'social') %>%
  subset(Competitive == 1) %>%
  summarySEwithin( measurevar="mean", withinvars="run",
                        idvar="SubjID", na.rm=FALSE, conf.interval=.95) %>%
  mutate(Competitive = 'Competitive') %>%
  rbind(noncomp.social.mean)

socialMean <- ggplot(social.mean, aes(x=factor(run), y=mean, fill=Competitive, group=Competitive)) +
    geom_errorbar(width=.1, aes(ymin=mean-ci, ymax=mean+ci,color=Competitive),alpha = 0.7) +
    geom_point(aes(color = Competitive)) + 
    geom_line(aes(color = Competitive)) +
    ggtitle('Average Mean of Other distributions (prior to run)') + 
    theme(plot.title = element_text(hjust = 0.5))


noncomp.social.SD <- Allsubs.meanSD %>%
  subset(type == 'social') %>%
  subset(Competitive == 0) %>%
  summarySEwithin( measurevar="SD", withinvars="run",
                        idvar="SubjID", na.rm=FALSE, conf.interval=.95) %>%
  mutate(Competitive = 'Non-Competitive')

social.SD <- Allsubs.meanSD %>%
  subset(type == 'social') %>%
  subset(Competitive == 1) %>%
  summarySEwithin( measurevar="SD", withinvars="run",
                        idvar="SubjID", na.rm=FALSE, conf.interval=.95) %>%
  mutate(Competitive = 'Competitive') %>%
  rbind(noncomp.social.SD)

socialSD <- ggplot(social.SD, aes(x=factor(run), y=SD, fill=Competitive, group=Competitive)) +
    geom_errorbar(width=.1, aes(ymin=SD-ci, ymax=SD+ci,color=Competitive),alpha = 0.7) +
    geom_point(aes(color = Competitive)) + 
    geom_line(aes(color = Competitive)) +
    ggtitle('Average SD of Other distributions (prior to run)') + 
    theme(plot.title = element_text(hjust = 0.5))

multiplot(socialMean,socialSD, cols=1)

```

### 3. Average adjusted pumps (error bars between-group standard error)
```{r, message=FALSE, warning=FALSE}

Allsubs.data %>%
  subset(P1_endState == 1) %>%
  subset(Game == 0) %>%
  subset(Run != 0) %>%
  mutate(Competitive = ifelse(Competitive == 0,'Non-Competitive','Competitive')) %>%
  summarySE(measurevar="maxP1_Tokens", groupvars=c("Run","Competitive")) %>%
  ggplot(aes(x=Run, y=maxP1_Tokens, colour=Competitive)) + 
  geom_errorbar(aes(ymin=maxP1_Tokens-se, ymax=maxP1_Tokens+se), width=.1) +
  geom_line() +
  geom_point() +
  ggtitle('Average Alone Adjusted pumps by condition') + 
  theme(plot.title = element_text(hjust = 0.5)) +
  ylab('Avg. Adjusted pumps') +
  ylim(20,32.5)


Allsubs.data %>%
  subset(P1_endState == 1) %>%
  subset(Game == 1) %>%
  subset(Run != 0) %>%
  mutate(Competitive = ifelse(Competitive == 0,'Non-Competitive','Competitive')) %>%
  summarySE(measurevar="maxP1_Tokens", groupvars=c("Run","Competitive")) %>%
  ggplot(aes(x=Run, y=maxP1_Tokens, colour=Competitive)) + 
  geom_errorbar(aes(ymin=maxP1_Tokens-se, ymax=maxP1_Tokens+se), width=.1) +
  geom_line() +
  geom_point() +
  ggtitle('Average Social Adjusted pumps by condition') + 
  theme(plot.title = element_text(hjust = 0.5)) +
  ylab('Avg. Adjusted pumps') +
  ylim(20,32.5)


```



```{r}

Allsubs.data %>%
  subset(Run == 1) %>%
  subset(Game == 0) %>%
  subset(P1_endState == 1) %>%
  mutate(SubjectID = factor(SubjectID)) %>%
  ggplot(aes(x = SubjectID, y = maxP1_Tokens)) + 
  geom_boxplot() +
  ggtitle('Run1 alone adjusted pumps by subject') +
  theme(plot.title = element_text(hjust = 0.5)) +
  ylab('Adjusted pumps')

Allsubs.data %>%
  subset(Run == 2) %>%
  subset(Game == 0) %>%
  subset(P1_endState == 1) %>%
  mutate(SubjectID = factor(SubjectID)) %>%
  ggplot(aes(x = SubjectID, y = maxP1_Tokens)) + 
  geom_boxplot() +
  ggtitle('Run1 alone adjusted pumps by subject') +
  theme(plot.title = element_text(hjust = 0.5)) +
  ylab('Adjusted pumps')

Allsubs.data %>%
  subset(Run == 3) %>%
  subset(Game == 0) %>%
  subset(P1_endState == 1) %>%
  mutate(SubjectID = factor(SubjectID)) %>%
  ggplot(aes(x = SubjectID, y = maxP1_Tokens)) + 
  geom_boxplot() +
  ggtitle('Run1 alone adjusted pumps by subject') +
  theme(plot.title = element_text(hjust = 0.5)) +
  ylab('Adjusted pumps')

Allsubs.data %>%
  subset(Run == 4) %>%
  subset(Game == 0) %>%
  subset(P1_endState == 1) %>%
  mutate(SubjectID = factor(SubjectID)) %>%
  ggplot(aes(x = SubjectID, y = maxP1_Tokens)) + 
  geom_boxplot() +
  ggtitle('Run1 alone adjusted pumps by subject') +
  theme(plot.title = element_text(hjust = 0.5)) +
  ylab('Adjusted pumps')

Allsubs.data %>%
  subset(Run == 5) %>%
  subset(Game == 0) %>%
  subset(P1_endState == 1) %>%
  mutate(SubjectID = factor(SubjectID)) %>%
  ggplot(aes(x = SubjectID, y = maxP1_Tokens)) + 
  geom_boxplot() +
  ggtitle('Run1 alone adjusted pumps by subject') +
  theme(plot.title = element_text(hjust = 0.5)) +
  ylab('Adjusted pumps')

Allsubs.data %>%
  subset(Run == 6) %>%
  subset(Game == 0) %>%
  subset(P1_endState == 1) %>%
  mutate(SubjectID = factor(SubjectID)) %>%
  ggplot(aes(x = SubjectID, y = maxP1_Tokens)) + 
  geom_boxplot() +
  ggtitle('Run1 alone adjusted pumps by subject') +
  theme(plot.title = element_text(hjust = 0.5)) +
  ylab('Adjusted pumps')
```

```{r}

Allsubs.data %>%
  subset(Competitive == 1) %>%
  subset(P1_endState == 1) %>%
  subset(P2_endState == 0) %>%
  subset(Game == 1) %>%
  mutate(maxP2_Tokens = factor(maxP2_Tokens)) %>%
  ggplot(aes(x = maxP2_Tokens, y= maxP1_Tokens)) +
  geom_boxplot()+ 
  ggtitle('P1 end state conditioanl on P2 pop \nCompetitive') +
  theme(plot.title = element_text(hjust = 0.5)) +
  ylab('Adjusted pumps') + xlab('P2 pumps at pop')


Allsubs.data %>%
  subset(Competitive == 0) %>%
  subset(P1_endState == 1) %>%
  subset(P2_endState == 0) %>%
  subset(Game == 1) %>%
  mutate(maxP2_Tokens = factor(maxP2_Tokens)) %>%
  ggplot(aes(x = maxP2_Tokens, y= maxP1_Tokens)) +
  geom_boxplot()+ 
  ggtitle('P1 end state conditioanl on P2 pop \nNon-competitive') +
  theme(plot.title = element_text(hjust = 0.5)) +
  ylab('Adjusted pumps') + xlab('P2 pumps at pop')


```
